Technical Report

### 2018-03-07 fully-abstract-comp/technical-report.tex
Fixes and typos in memory satisfaction.
Small rephrasing.
Rename heap relation for standard region to something recognizable.
Some work on a lemma about the read and write condition. Add some remarks about problems with spurious later modalities.

For convenience, we will add the convention that the memory update $\update{\mem.a}{\scall{o}{r_1}{r_2}}$ corresponds to
\[
  \begin{array}{l}
    \update{\mem.a}{\scall[0]{o}{r_1}{r_2}}\\
    \update{\mem.a}{\scall[1]{o}{r_1}{r_2}}\\
    \dots\\
    \update{\mem.a}{\scall[\calllen-1]{o}{r_1}{r_2}}\\
  \end{array}
\]

@@

@@

\subsection{Memory satisfaction}
\lau{14-02-2018: No matter what the memory satisfaction ends up looking like, remember to handle the revoked case.}
{\color{DarkGreen}
Memory satisfaction for new worlds:
\[
  \memSat{\ms_S,\ms_\stk,\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      \stk = (\opc_0,\ms_0):: \dots :: (\opc_m,\ms_m) \wedge \\
      \ms_S \uplus \ms_\stk \uplus \ms_0 \uplus \dots \uplus \ms_m  \wedge\\
      W = W_{\var{stack}} \uplus W_{\var{free\_stack}} \uplus W_{\var{heap}} \wedge\\
      \exists \ms_\var{T,stack}, \ms_\var{T,free\_stack}, \ms_\var{T,heap}\ldotp \\
      \quad \ms_T = \ms_\var{T,stack} \uplus \ms_\var{T,free\_stack} \uplus \ms_\var{T,heap} \wedge \\
      \quad \memSatStack{\stk,\ms_\var{T,stack}}{W_{\var{stack}}} \wedge \\
      \quad \memSatFStack{\ms_\stk,\ms_\var{T,free\_stack}}{W_{\var{free\_stack}}} \wedge \\
      \quad \memSatHeap{\ms_S,\ms_\var{T,heap}}{W_{\var{heap}}}
    \end{array}
  \right.
\]

\[
  \memSatStack{\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      W_\var{stack} = \pwpriv \wedge \\
      \stk = (\opc_0,\ms_0), \dots (\opc_m,\ms_m) \wedge \\
      \exists R_\ms : \dom(\activeReg{W_\var{stack}}) \fun \MemSeg \times \SealableCaps \times \MemSeg \ldotp \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{W_\var{stack}})} \pi_3(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{W_\var{stack}}) \fun \World \ldotp \\
      \qquad W = \bigoplus_{r \in \dom(\activeReg{W_\var{stack}})} R_W(r) \wedge \\
      \qquad \forall r \in \dom(\activeReg{W_\var{stack}}), n' < n \ldotp \\
      \qquad \quad \npair[n']{(\pi_1(R_\ms(r)),\pi_3(R_\ms(r))} \in W_\var{stack}(r).H \; W_\var{stack}(r).s \; \xi^{-1}(R_W(r)) \\
      \qquad \quad \pi_2(R_\ms(r)) = W_\var{stack}(r).\opc \wedge\\
      \qquad \quad \exists i \ldotp \opc_i = W_\var{stack}(r).\opc \wedge \ms_i = \pi_1 (R_\ms(r))
    \end{array}
  \right.
\]

@@

\[
  \memSatHeap{ms,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      W_\var{heap} = \pwheap \wedge \\
      \exists R_\ms : \dom(\activeReg{W_\var{heap}}) \fun \MemSeg \times \MemSeg \wedge \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{W_\var{heap}})} \pi_2(R_\ms(r)) \wedge \\
      \quad \ms = \biguplus_{r \in \dom(\activeReg{W_\var{heap}})} \pi_1(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{W_\var{heap}}) \fun \World\ldotp\\
      \qquad W = \oplus_{r \in \dom(\activeReg{W_\var{heap}})} R_W(r) \wedge\\
      \qquad \forall r \in \activeReg{W_\var{heap}}, n' < n \ldotp \\
      \qquad \quad \npair[n']{R_\ms(r)} \in  W_\var{heap}(r).H \; W_\var{stack}(r).s \; \xi^{-1}(R_W(r))
    \end{array}
  \right.
\]
}

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
Two expression relations: one for sealed code-data pairs being jumped to and one for capabilities being jumped to in the regular way.
The argument for having one relation relate pairs of pairs of capabilties and the other relate pairs of capabilities is that that is how xjump and regular jumps work: xjump takes pairs while regular jumps take single capabilities.
\begin{align*}
  \lrexj(W) &= \left\{ \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrr, W_\lrm \ldotp \\
      \qquad\npair[n']{[\stpair[.]{v_{c,S}}{v_{c,T}},\stpair[.]{v_{d,T}}{v_{d,S}}]} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrr) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)}\\
      \qquad \Phi_S' = \xjumpResult{v_{c,S}}{v_{d,S}}{\Phi_S}\\
      \qquad\Phi_T = (\ms_T,\reg_T)\\
      \qquad\Phi_T' = \xjumpResult{v_{c,T}}{v_{d,T}}{\Phi_T}\\
      \qquad W \oplus W_\lrr \oplus W_\lrm \\
      \qquad\Rightarrow\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
    \end{array}
    \right\}\\
  \lre(W) &= \left\{ \npair{\stpair[.]{v_{c,S}}{v_{c,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrr, W_\lrm \ldotp \\
      \qquad\npair[n']{[\stpair[.]{v_{c,S}}{v_{c,T}}]} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrr) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)}\\
      \qquad \Phi_S' = \Phi_S \updReg{\pcreg}{v_{c,S}}\\
      \qquad\Phi_T = (\ms_T,\reg_T)\\
      \qquad\Phi_T' = \Phi_T\updReg{\pcreg}{v_{c,T}}\\
      \qquad W \oplus W_\lrr \oplus W_\lrm\\
      \qquad\Rightarrow\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
    \end{array}
    \right\}
\end{align*}

\[
  \lro = \left\{ \npair{\left(\array{l}\src{(\ms_S,\reg_S,\stk_S,\ms_{\stk,S})},\\(\ms_T,\reg_T)\endarray\right)} \middle|
    \begin{array}{l}
      \forall i \leq n, \src{\ms_{f,S}}, \ms_{f,T} \ldotp \\
      \quad \src{(\ms_S \uplus \ms_{f,S},\reg_S,\stk_S,\ms_{\stk,S})} \term[i] \Rightarrow (\ms_T \uplus \ms_{f,T},\reg_T) \term\\
      \quad \tand\\
      \quad (\ms_T \uplus \ms_{f,T},\reg_T) \term[i] \Rightarrow \src{(\ms_S \uplus \ms_{f,S},\reg_S,\stk_S,\ms_{\stk,S})} \term
    \end{array}
\right\}
\]

@@

\subsection{Permission based conditions}
\[
  \addressable{\lin,W} =
  \begin{cases}
    \{ r \mid W(r) = (\pure,\_) \} & \text{if $\lin = \normal$} \\
    \{ r \mid W(r) = (\spatialo,\_) \}  & \text{otherwise (i.e. $\lin = \linear$)} \\
  \end{cases}
\]

\[
  \readCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad W(r) \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad W(r) \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, W}, \ms \ldotp\\
      \quad \dom(\ms) \supseteq [\baddr,\eaddr] \wedge \\
      \quad W(r) \nequal \stareg[(\ms,\ms)]{\pur}
    \end{array}
  \right\}
\]

@@

\[
  \writeCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr)}) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad W(r) \nsupeq[n-1] \stdreg{[\baddr',\eaddr']}{\pur} \wedge \\
      \qquad W(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackWriteCond{W} = \left\{ \npair{(\baddr,\eaddr)}) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad W(r) \nsupeq[n-1] \stdreg{[\baddr',\eaddr']}{\pur} \wedge \\
      \qquad W(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.

@@

\subsection{Standard regions}
\label{sec:standard-regions}
Standard region:
\[
  \stdreg{A}{v} \defeq (v,*,=,=,H_A)
\]
for readability, we use $\spao$ short for $\spatialo$, $\spa$ short for $\spatial$, and $\pur$ as short for $\pure$.
\lau{02-11-2017: I am not sure whether it should be a $\normal$ region. In previous work $\nsubeq$ ignored the ``view'' which it may also do here, and then then it does not matter which one it is.}
where $H_A$ is defined as follows:
\[
  H_A \; s \; \hat{W} \defeq \left\{ \npair{\ms_S,\ms_T} \middle|
    \begin{array}{l}
      \dom(\ms_S) = \dom(\ms_T) = A \wedge \\
      \exists S : \dom(\ms_S) \fun \World \ldotp \xi(W) = \oplus_{\aaddr \in \dom(\ms_S)} S(\aaddr) \wedge\\
      \quad \forall \aaddr \in A \ldotp \npair[n-1]{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))
    \end{array}
  \right\}
\]
\lau{01-11-2017: TODO look into what kind of world separation should happen here.}

>>>>

For convenience, we will add the convention that the memory update $\update{\mem.a}{\scall{o}{r_1}{r_2}}$ corresponds to
\[
  \begin{array}{l}
    \update{\mem.a}{\scall[0]{o}{r_1}{r_2}}\\
    \update{\mem.a+1}{\scall[1]{o}{r_1}{r_2}}\\
    \dots\\
    \update{\mem.a+\calllen-1}{\scall[\calllen-1]{o}{r_1}{r_2}}\\
  \end{array}
\]

@@

\begin{lemma}
  $\oplus$ is associative and commutative.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

@@

\subsection{Memory satisfaction}
\lau{14-02-2018: No matter what the memory satisfaction ends up looking like, remember to handle the revoked case.}
{\color{DarkGreen}
Memory satisfaction for new worlds:
\[
  \memSat{\ms_S,\ms_\stk,\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      \stk = (\opc_0,\ms_0):: \dots :: (\opc_m,\ms_m) \wedge \\
      \ms_S \uplus \ms_\stk \uplus \ms_0 \uplus \dots \uplus \ms_m  \wedge\\
      W = W_{\var{stack}} \oplus W_{\var{free\_stack}} \oplus W_{\var{heap}} \wedge\\
      \exists \ms_\var{T,stack}, \ms_\var{T,free\_stack}, \ms_\var{T,heap}\ldotp \\
      \quad \ms_T = \ms_\var{T,stack} \uplus \ms_\var{T,free\_stack} \uplus \ms_\var{T,heap} \wedge \\
      \quad \memSatStack{\stk,\ms_\var{T,stack}}{W_{\var{stack}}} \wedge \\
      \quad \memSatFStack{\ms_\stk,\ms_\var{T,free\_stack}}{W_{\var{free\_stack}}} \wedge \\
      \quad \memSatHeap{\ms_S,\ms_\var{T,heap}}{W_{\var{heap}}}
    \end{array}
  \right.
\]

\[
  \memSatStack{\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      W_\var{stack} = \pwpriv \wedge \\
      \stk = (\opc_0,\ms_0), \dots (\opc_m,\ms_m) \wedge \\
      \exists R_\ms : \dom(\activeReg{W_\var{stack}}) \fun \MemSeg \times \SealableCaps \times \MemSeg \ldotp \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{W_\var{stack}})} \pi_3(R_\ms(r)) \wedge \\
      \quad \ms_0 \uplus \dots \uplus \ms_m = \biguplus_{r \in \dom(\activeReg{W_\var{stack}})} \pi_1(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{W_\var{stack}}) \fun \World \ldotp \\
      \qquad W = \bigoplus_{r \in \dom(\activeReg{W_\var{stack}})} R_W(r) \wedge \\
      \qquad \forall r \in \dom(\activeReg{W_\var{stack}}), n' < n \ldotp \\
      \qquad \quad \npair[n']{(\pi_1(R_\ms(r)),\pi_3(R_\ms(r))} \in W_\var{stack}(r).H \; W_\var{stack}(r).s \; \xi^{-1}(R_W(r)) \\
      \qquad \quad \pi_2(R_\ms(r)) = W_\var{stack}(r).\opc \wedge\\
      \qquad \quad \exists i \ldotp \opc_i = W_\var{stack}(r).\opc \wedge \ms_i = \pi_1 (R_\ms(r))
    \end{array}
  \right.
\]

@@

\[
  \memSatHeap{ms,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      \exists R_\ms : \dom(\activeReg{\pwheap}) \fun \MemSeg \times \MemSeg \wedge \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{\pwheap})} \pi_2(R_\ms(r)) \wedge \\
      \quad \ms = \biguplus_{r \in \dom(\activeReg{\pwheap})} \pi_1(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{\pwheap}) \fun \World\ldotp\\
      \qquad W = \oplus_{r \in \dom(\activeReg{\pwheap})} R_W(r) \wedge\\
      \qquad \forall r \in \activeReg{\pwheap}, n' < n \ldotp \\
      \qquad \quad \npair[n']{R_\ms(r)} \in  \pwheap(r).H \; \pwheap(r).s \; \xi^{-1}(R_W(r))
    \end{array}
  \right.
\]
}

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
Two expression relations: one for sealed code-data pairs being jumped to and one for capabilities being jumped to in the regular way.
The argument for having one relation relate pairs of pairs of capabilties and the other relate pairs of capabilities is that that is how xjump and regular jumps work: xjump takes pairs while regular jumps take single capabilities.
\begin{align*}
  \lrexj(W) &= \left\{ \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrrs , W_\lrm \ldotp \\
      \qquad\npair[n']{[\stpair[.]{v_{c,S}}{v_{c,T}},\stpair[.]{v_{d,T}}{v_{d,S}}]} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr (W_\lrrs ) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)}\\
      \qquad \Phi_S' = \xjumpResult{v_{c,S}}{v_{d,S}}{\Phi_S}\\
      \qquad\Phi_T = (\ms_T,\reg_T)\\
      \qquad\Phi_T' = \xjumpResult{v_{c,T}}{v_{d,T}}{\Phi_T}\\
      \qquad W \oplus W_\lrrs \oplus W_\lrm \\
      \qquad\Rightarrow\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
    \end{array}
    \right\}\\
  \lre(W) &= \left\{ \npair{\stpair[.]{v_{c,S}}{v_{c,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrrs , W_\lrm \ldotp \\
      \qquad\npair[n']{[\stpair[.]{v_{c,S}}{v_{c,T}}]} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr (W_\lrrs ) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)}\\
      \qquad \Phi_S' = \Phi_S \updReg{\pcreg}{v_{c,S}}\\
      \qquad\Phi_T = (\ms_T,\reg_T)\\
      \qquad\Phi_T' = \Phi_T\updReg{\pcreg}{v_{c,T}}\\
      \qquad W \oplus W_\lrrs \oplus W_\lrm\\
      \qquad\Rightarrow\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
    \end{array}
    \right\}
\end{align*}

\[
  \lrol = \left\{ \npair{\left(\array{l}\src{(\ms_S,\reg_S,\stk_S,\ms_{\stk,S})},\\(\ms_T,\reg_T)\endarray\right)} \middle|
    \begin{array}{l}
      \forall i \leq n, \src{\ms_{f,S}}, \ms_{f,T} \ldotp \\
      \quad \src{(\ms_S \uplus \ms_{f,S},\reg_S,\stk_S,\ms_{\stk,S})} \term[i] \Rightarrow (\ms_T \uplus \ms_{f,T},\reg_T) \term\\
    \end{array}
\right\}
\]
\[
  \lror = \left\{ \npair{\left(\array{l}\src{(\ms_S,\reg_S,\stk_S,\ms_{\stk,S})},\\(\ms_T,\reg_T)\endarray\right)} \middle|
    \begin{array}{l}
      \forall i \leq n, \src{\ms_{f,S}}, \ms_{f,T} \ldotp \\
      \quad (\ms_T \uplus \ms_{f,T},\reg_T) \term[i] \Rightarrow \src{(\ms_S \uplus \ms_{f,S},\reg_S,\stk_S,\ms_{\stk,S})} \term
    \end{array}
\right\}
\]

@@

\subsection{Permission based conditions}
\lau{28-02-2018: These definitions need to be updated to fit with the new worlds}.
\[
  \addressable{\lin,W} =
  \begin{cases}
    \{ r \mid W(r) = (\pure,\_) \} & \text{if $\lin = \normal$} \\
    \{ r \mid W(r) = (\spatialo,\_) \}  & \text{otherwise (i.e. $\lin = \linear$)} \\
  \end{cases}
\]

\[
  \readCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad \pwheap(r) \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad \pwfree(r) \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, \pwheap}, \ms \ldotp\\
      \quad \dom(\ms) \supseteq [\baddr,\eaddr] \wedge \\
      \quad \pwheap(r) \nequal \stareg[(\ms,\ms)]{\pur}
    \end{array}
  \right\}
\]

@@

\[
  \writeCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr)}) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad \pwheap(r) \nsupeq[n-1] \stdreg{[\baddr',\eaddr']}{\pur} \wedge \\
      \qquad \pwheap(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\dominique{Why $n-1$ above?  There is already a quantification over $n' <n$ in the memory satisfaction relation and another $n-1$ is used in $\stdreg{[\baddr',\eaddr']}{\pur}$. Also: readCond doesn't have the $n-1$.}
\[
  \stackWriteCond{W} = \left\{ \npair{(\baddr,\eaddr)}) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad \pwheap(r) \nsupeq[n-1] \stdreg{[\baddr',\eaddr']}{\pur} \wedge \\
      \qquad \pwheap(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.

@@

\subsection{Standard regions}
\label{sec:standard-regions}
Standard region:
\[
  \stdreg{A}{v} \defeq (v,*,=,=,H_A^{\mathrm{std}})
\]
for readability, we use $\spao$ short for $\spatialo$, $\spa$ short for $\spatial$, and $\pur$ as short for $\pure$.
\lau{02-11-2017: I am not sure whether it should be a $\normal$ region. In previous work $\nsubeq$ ignored the ``view'' which it may also do here, and then then it does not matter which one it is.}
where $H_A$ is defined as follows:
\[
  H_A^{\mathrm{std}} \; * \; \hat{W} \defeq \left\{ \npair{\ms_S,\ms_T} \middle|
    \begin{array}{l}
      \dom(\ms_S) = \dom(\ms_T) = A \wedge \\
      \exists S : A \fun \World \ldotp \xi(W) = \oplus_{\aaddr \in A} S(\aaddr) \wedge\\
      \quad \forall \aaddr \in A \ldotp \npair[n-1]{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))
    \end{array}
  \right\}
\]
\lau{01-11-2017: TODO look into what kind of world separation should happen here.}
\dominique{7-3-2018: is it necessary to have $n-1$ above? there is already a quantification over $n'<n$ in the memory satisfaction relation.}
